### 2023-08-11 appendices/appendix_benchmarking.tex
Finalize model-agnostic paper and add stroke paper
Add automated medical coding paper etc

\chapter[supplementary material for benchmarking generative latent variable models for speech]{Supplementary material for Benchmarking generative latent variable models for speech}
\label{app:benchmarking}
\ifthenelse{\equal{\skipappendices}{true}}{}{

@@

@@

    \end{tabular}
    \vspace{2mm}

@@

        % % x to s first layer
        \edge[]{s_1_1}{x_1};
        \edge[]{s_1_2}{x_2};
        \edge[]{s_1_3}{x_3};
        \edge[]{s_1_4}{x_4};
        \edge[]{s_1_5}{x_5};
        \edge[]{s_1_6}{x_6};
        \edge[]{s_1_7}{x_7};
        \edge[]{s_1_8}{x_8};

        % % s per layer forward in time
        \edge[blue]{s_1_1}{s_1_2};
        \edge[blue]{s_1_2}{s_1_3};
        \edge[blue]{s_1_3}{s_1_4};
        \edge[blue]{s_1_4}{s_1_5};
        \edge[blue]{s_1_5}{s_1_6};
        \edge[blue]{s_1_6}{s_1_7};
        \edge[blue]{s_1_7}{s_1_8};

@@

        % % s across layers on time
        \edge[blue]{s_2_1}{s_1_1};
        \edge[blue]{s_2_3}{s_1_3};
        \edge[blue]{s_2_5}{s_1_5};
        \edge[blue]{s_2_7}{s_1_7};

@@

        % % s across layers forward in time
        \edge[blue]{s_2_1}{s_1_2};
        \edge[blue]{s_2_3}{s_1_4};
        \edge[blue]{s_2_5}{s_1_6};
        \edge[blue]{s_2_7}{s_1_8};

@@

        % \node[above=of s_3_5, yshift=-1.cm, xshift=-2cm] (phi) {$p_\theta(\xb,\zb)$};
    \end{tikzpicture}
    \hspace{2cm}
    }
    \caption{}
    \label{fig: cwvae three-layered graphical model generative}
    \end{subfigure}
    \\
    \vspace{0.25cm}
    \\
    \begin{subfigure}[b]{\textwidth}
    \flushright
    \def\col{blue}
    \resizebox{!}{5.3cm}{
    \begin{tikzpicture}
        % INFERENCE
        % nodes
        \node[obs] (x_1) {$\xb_t$};%
        \node[obs,right=1.00cm of x_1] (x_2) {$\xb_{t+1}$};%
        \node[obs,right=1.00cm of x_2] (x_3) {$\xb_{t+2}$};%
        \node[obs,right=1.00cm of x_3] (x_4) {$\xb_{t+3}$};%
        \node[obs,right=1.00cm of x_4] (x_5) {$\xb_{t+4}$};%
        \node[obs,right=1.00cm of x_5] (x_6) {$\xb_{t+5}$};%
        \node[obs,right=1.00cm of x_6] (x_7) {$\xb_{t+6}$};%
        \node[obs,right=1.00cm of x_7] (x_8) {$\xb_{t+7}$};%

>>>>

\chapter[supplementary material: benchmarking generative latent variable models for speech]{Supplementary material: Benchmarking generative latent variable models for speech}
\label{app:benchmarking}
\ifthenelse{\equal{\skipappendices}{true}}{}{

@@

    \resizebox*{!}{\textheight}{

@@

    \end{tabular}%

@@

        % x to s first layer
        \edge[]{s_1_1}{x_1};
        \edge[]{s_1_2}{x_2};
        \edge[]{s_1_3}{x_3};
        \edge[]{s_1_4}{x_4};
        \edge[]{s_1_5}{x_5};
        \edge[]{s_1_6}{x_6};
        \edge[]{s_1_7}{x_7};
        \edge[]{s_1_8}{x_8};

        % s per layer forward in time
        \edge[blue]{s_1_1}{s_1_2};
        \edge[blue]{s_1_2}{s_1_3};
        \edge[blue]{s_1_3}{s_1_4};
        \edge[blue]{s_1_4}{s_1_5};
        \edge[blue]{s_1_5}{s_1_6};
        \edge[blue]{s_1_6}{s_1_7};
        \edge[blue]{s_1_7}{s_1_8};

@@

        % s across layers on time
        \edge[blue]{s_2_1}{s_1_1};
        \edge[blue]{s_2_3}{s_1_3};
        \edge[blue]{s_2_5}{s_1_5};
        \edge[blue]{s_2_7}{s_1_7};

@@

        % s across layers forward in time
        \edge[blue]{s_2_1}{s_1_2};
        \edge[blue]{s_2_3}{s_1_4};
        \edge[blue]{s_2_5}{s_1_6};
        \edge[blue]{s_2_7}{s_1_8};

@@

        % \node[above=of s_3_5, yshift=-1.cm, xshift=-2cm] (phi) {$p_\theta(\xb,\zb)$};
    \end{tikzpicture}
    % \hspace{2cm}
    }
    \caption{}
    \label{fig: cwvae three-layered graphical model generative}
    \end{subfigure}
    \\
    \vspace{0.25cm}
    \\
    \begin{subfigure}[b]{\textwidth}
    \flushright
    \def\col{blue}
    \resizebox{!}{5.3cm}{
    \begin{tikzpicture}
        % INFERENCE
        % nodes
        \node[obs] (x_1) {$\xb_t$};%
        \node[obs,right=1.00cm of x_1] (x_2) {$\xb_{t+1}$};%
        \node[obs,right=1.00cm of x_2] (x_3) {$\xb_{t+2}$};%
        \node[obs,right=1.00cm of x_3] (x_4) {$\xb_{t+3}$};%
        \node[obs,right=1.00cm of x_4] (x_5) {$\xb_{t+4}$};%
        \node[obs,right=1.00cm of x_5] (x_6) {$\xb_{t+5}$};%
        \node[obs,right=1.00cm of x_6] (x_7) {$\xb_{t+6}$};%
        \node[obs,right=1.00cm of x_7] (x_8) {$\xb_{t+7}$};%

### 2023-08-11 appendices/appendix_modelagnostic.tex
Add automated medical coding paper etc

\chapter[supplementary material for model-agnostic out-of-distribution detection using combined statistical tests]{Supplementary material for Model-Agnostic Out-of-Distribution Detection Using Combined Statistical Tests}
\label{app:modelagnostic}
\ifthenelse{\equal{\skipappendices}{true}}{}{

>>>>

\chapter[supplementary material: model-agnostic out-of-distribution detection using combined statistical tests]{Supplementary material: Model-Agnostic Out-of-Distribution Detection Using Combined Statistical Tests}
\label{app:modelagnostic}
\ifthenelse{\equal{\skipappendices}{true}}{}{

### 2023-08-11 appendices/appendix_retrospective.tex
Add automated medical coding paper etc

\chapter[supplementary material for a retrospective study on machine learning-assisted stroke recognition for medical helpline calls]{Supplementary Material for A Retrospective Study on Machine Learning-Assisted Stroke Recognition for Medical Helpline Calls}
\label{app:retrospective}
\ifthenelse{\equal{\skipappendices}{true}}{}{

@@

\todo[inline]{Insert table A2 here}
\begin{table}[h]
    \centering
    \caption{}
    \label{tab_retrospective:tableA2}
    % \resizebox*{0.98\textwidth}{!}{%
    % \begin{tabular}{l|l|l}
    %     \toprule

    %     \midrule

    %     \bottomrule
    % \end{tabular}%
    % }
\end{table}

\todo[inline]{Insert table A3 here}
\begin{table}[h]
    \centering
    \caption{}
    \label{tab_retrospective:tableA3}
    % \resizebox*{0.98\textwidth}{!}{%
    % \begin{tabular}{l|l|l}
    %     \toprule

    %     \midrule

    %     \bottomrule
    % \end{tabular}%
    % }
\end{table}

@@

\todo[inline]{Insert table A4 here}
\begin{table}[h]
    \centering
    \caption{}
    \label{tab_retrospective:tableA4}
    % \resizebox*{0.98\textwidth}{!}{%
    % \begin{tabular}{l|l|l}
    %     \toprule

    %     \midrule

    %     \bottomrule
    % \end{tabular}%
    % }
\end{table}

\todo[inline]{Insert table A5 here}
\begin{table}[h]
    \centering
    \caption{}
    \label{tab_retrospective:tableA5}
    % \resizebox*{0.98\textwidth}{!}{%
    % \begin{tabular}{l|l|l}
    %     \toprule

    %     \midrule

    %     \bottomrule
    % \end{tabular}%
    % }
\end{table}

@@

\todo[inline]{Insert table A6 here}
\begin{table}[h]
    \centering
    \caption{}
    \label{tab_retrospective:tableA6}
    % \resizebox*{0.98\textwidth}{!}{%
    % \begin{tabular}{l|l|l}
    %     \toprule

    %     \midrule

    %     \bottomrule
    % \end{tabular}%
    % }
\end{table}

@@

>>>>

\chapter[supplementary material: a retrospective study on machine learning-assisted stroke recognition for medical helpline calls]{Supplementary Material for: A Retrospective Study on Machine Learning-Assisted Stroke Recognition for Medical Helpline Calls}
\label{app:retrospective}
\ifthenelse{\equal{\skipappendices}{true}}{}{

@@

% \todo[inline]{Insert table A2 here}
\begin{table}[h]
    \centering
    \caption{Model performance based on sex and age [mean (95\% CI)] when 1-1-2 training data is not used for training.}
    \label{tab_retrospective:tableA2}
    % \resizebox*{0.98\textwidth}{!}{%
    \begin{tabular}{l|cc|cc}
        \toprule

         & \multicolumn{2}{c|}{Model} & \multicolumn{2}{c}{Model} \\
        \midrule
         & Female & Male & 18-64 years & 65+ years \\

        F1-score [\%] $\uparrow$ & \makecell{28.7 \\ (27.8-29.6)} & \makecell{36.2 \\ (35.3-37.2)} & \makecell{20.5 \\ (19.5-21.5)} & \makecell{39.4 \\ (38.6-40.3)} \\
        \midrule
        Sensitivity [\%] $\uparrow$ & \makecell{58.2 \\ (56.7-59.9)} & \makecell{62.1 \\ (60.7-63.6)} & \makecell{53.0 \\ (50.9-55.0)} & \makecell{63.0 \\ (61.9-64.3)} \\
        \midrule
        PPV [\%] $\uparrow$ & \makecell{19.0 \\ (18.3-19.7)} & \makecell{25.6 \\ (24.8-26.4)} & \makecell{12.7 \\ (12.0-13.4)} & \makecell{28.7 \\ (27.9-29.5)} \\
        \midrule
        \makecell[l]{FOR [\%] $\downarrow$ \\ (1 - specificity)}  & \makecell{0.077 \\ (0.073-0.080)} & \makecell{0.102 \\ (0.097-0.106)} & \makecell{0.034 \\ (0.032-0.036)} & \makecell{0.318 \\ (0.305-0.331)} \\
        \midrule
        \makecell[l]{FPR [\%] $\downarrow$ \\ (1 - NPV)} & \makecell{0.45 \\ (0.446-0.463)} & \makecell{0.483 \\ (0.473-0.494)} & \makecell{0.264 \\ (0.258-0.270)} & \makecell{1.335 \\ (1.308-1.362)} \\

        \bottomrule
    \end{tabular}%
    % }
\end{table}

% \todo[inline]{Insert table A3 here}
\begin{table}[h]
    \centering
    \caption{Model performance based on sex and age [mean (95\% CI)] on the 2021 data without diagnostic category.}
    \label{tab_retrospective:tableA3}
    % \resizebox*{0.98\textwidth}{!}{%
    \begin{tabular}{l|cc|cc}
        \toprule

         & \multicolumn{2}{c|}{Model} & \multicolumn{2}{c}{Model} \\
        \midrule
         & Female & Male & 18-64 years & 65+ years \\

        F1-score [\%] $\uparrow$ & \makecell{30.4 \\ (29.3-31.5)} & \makecell{35.2 \\ (34.0-36.4)} & \makecell{24.3 \\ (23.0-25.7)} & \makecell{36.6 \\ (35.6-37.6)} \\
        \midrule
        Sensitivity [\%] $\uparrow$ & \makecell{44.5 \\ (42.9-46.0)} & \makecell{52.8 \\ (51.1-54.4)} & \makecell{45.6 \\ (43.4-47.9)} & \makecell{49.2 \\ (47.9-50.5)} \\
        \midrule
        PPV [\%] $\uparrow$ & \makecell{23.1 \\ (22.2-24.1)} & \makecell{26.4 \\ (25.3-27.4)} & \makecell{16.6 \\ (15.5-17.5)} & \makecell{29.1 \\ (28.2-30.0)} \\
        \midrule
        \makecell[l]{FOR [\%] $\downarrow$ \\ (1 - specificity)} & \makecell{0.152 \\ (0.146-0.159)} & \makecell{0.155 \\ (0.147-0.162)} & \makecell{0.058 \\ (0.055-0.062)} & \makecell{0.372 \\ (0.359-0.386)} \\
        \midrule
        \makecell[l]{FPR [\%] $\downarrow$ \\ (1 - NPV)} & \makecell{0.404 \\ (0.394-0.414)} & \makecell{0.480 \\ (0.467-0.494)} & \makecell{0.246 \\ (0.239-0.254)} & \makecell{0.873 \\ (0.852-0.894)} \\

        \bottomrule
    \end{tabular}%
    % }
\end{table}

@@

% % \todo[inline]{Insert table A4 here}
\begin{table}[h]
    \centering
    \caption{Mean impact for words with the largest positive rank score in calls predicted as stroke.}
    \label{tab_retrospective:tableA4}
    \resizebox*{\textwidth}{!}{%
    \begin{tabular}{l|llccc}
        \toprule
        \multicolumn{6}{c}{Stroke predictions, $D=1,897$} \\
        \midrule
         & Word, $w$ (\textit{Danish}) & Translation (\textit{English}) & Rank, $r^{(w)}$ & Occurences, $D^{(w)}$ & \makecell{Impact, $i^{(d,w)}$ \\ mean $\pm$ std.} \\
        \midrule    
        1. & Ambulance & Ambulance & $1.000$ & $1,$680 & $0.52 \pm 0.51$ \\
        2. & Blodprop & Blood clot & $0.599$ & $89$5 & $0.51 \pm 0.58$ \\
        3. & Venstre & Left & $0.381$ & $1,$108 & $0.38 \pm 0.4$ \\
        4. & Højre & Right & $0.326$ & $1,$050 & $0.31 \pm 0.42$ \\
        5. & Dobbeltsyn & Double vision & $0.247$ & $84$ & $1.01 \pm 1.26$ \\
        6. & Ordene & The words & $0.217$ & $34$4 & $0.6 \pm 0.45$ \\
        7. & Pludselig & Suddenly & $0.142$ & $78$3 & $0.29 \pm 0.28$ \\
        8. & Arm & Arm & $0.140$ & $70$9 & $0.3 \pm 0.3$ \\
        9. & Side & Side & $0.125$ & $1,$139 & $0.23 \pm 0.21$ \\
        10. & Apopleksi & Stroke & $0.102$ & $11$7 & $0.33 \pm 0.82$ \\
        11. & Dobbelt & Double & $0.102$ & $11$3 & $0.54 \pm 0.72$ \\
        12. & Styre & Control & $0.092$ & $13$4 & $0.63 \pm 0.46$ \\
        13. & Opkald & Call & $0.067$ & $39$ & $0.18 \pm 1.22$ \\
        14. & Følelsesløs & Numb & $0.065$ & $94$ & $0.53 \pm 0.58$ \\
        15. & Minutter & Minutes & $0.064$ & $76$3 & $0.22 \pm 0.16$ \\
        16. & Talebesvær & Difficulties speaking & $0.063$ & $44$ & $0.87 \pm 0.72$ \\
        17. & Hjerneblødning & Haemorrhagic stroke & $0.060$ & $13$3 & $0.4 \pm 0.49$ \\
        18. & Hånd & Hand & $0.057$ & $29$7 & $0.28 \pm 0.31$ \\
        19. & Ambulancen & The ambulance & $0.055$ & $52$1 & $0.21 \pm 0.23$ \\
        20. & Snøvler & Slurred speech & $0.052$ & $58$ & $0.71 \pm 0.54$ \\
        21. & Blodpropper & Blood clots & $0.051$ & $22$4 & $0.27 \pm 0.36$ \\
        22. & Hurtigt & Fast & $0.048$ & $66$3 & $0.18 \pm 0.18$ \\
        23. & Udtrykke & Express & $0.044$ & $44$ & $0.59 \pm 0.74$ \\
        24. & Blodfortyndende & Blood thinner & $0.044$ & $25$9 & $0.32 \pm 0.22$ \\
        25. & Usammenhængende & Incoherent & $0.043$ & $15$ & $1.14 \pm 1.13$ \\
        26. & Skæv & Lopsided & $0.039$ & $21$1 & $0.29 \pm 0.28$ \\
        27. & Nedsat & Reduced & $0.038$ & $52$8 & $0.14 \pm 0.21$ \\
        28. & Hænger & Hangs & $0.036$ & $62$8 & $0.15 \pm 0.17$ \\
        29. & Forbigående & Transient & $0.035$ & $48$ & $0.52 \pm 0.62$ \\
        30. & Vrøvler & Not making sense & $0.033$ & $14$ & $1.13 \pm 0.89$ \\
        \bottomrule
    \end{tabular}%
    }
\end{table}

% \todo[inline]{Insert table A5 here}
\begin{table}[h]
    \centering
    \caption{Mean impact for words with the largest negative rank score in calls predicted as non-stroke.}
    \label{tab_retrospective:tableA5}
    \resizebox*{\textwidth}{!}{%
    \begin{tabular}{l|llcrr}
        \toprule
        \multicolumn{6}{c}{Non-stroke predictions, $D=342,133$} \\
        \midrule
         & Word, $w$ (\textit{Danish}) & Translation (\textit{English}) & Rank, $r^{(w)}$ & Occurences, $D^{(w)}$ & \makecell{Impact, $i^{(d,w)}$ \\ mean $\pm$ std.} \\
        \midrule    
        1. & Stivkrampe & Tetanus & $-1.000$ & $4378$ & $-19.40 \pm 10.61$ \\
        2. & Gravid & Pregnant & $-0.901$ & $8749$ & $-12.08 \pm 8.64$ \\
        3. & Skåret & Cut & $-0.772$ & $7592$ & $-11.98 \pm 8.61$ \\
        4. & Forbinding & Bandage & $-0.569$ & $4561$ & $-12.87 \pm 10.08$ \\
        5. & Amager & Amager (a location) & $-0.566$ & $23776$ & $-5.60 \pm 4.43$ \\
        6. & Klokken & O'clock & $-0.535$ & $94436$ & $-2.22 \pm 2.69$ \\
        7. & Skadestuen & The emergency room & $-0.486$ & $42809$ & $-3.72 \pm 3.23$ \\
        8. & Politiet & The police & $-0.413$ & $2903$ & $-10.73 \pm 13.77$ \\
        9. & Hævet & Swollen & $-0.388$ & $60559$ & $-2.84 \pm 2.38$ \\
        10. & Håndkøb & over the counter (otc) & $-0.372$ & $4641$ & $-11.64 \pm 6.00$ \\
        11. & Halsen & The neck & $-0.366$ & $30151$ & $-3.33 \pm 3.86$ \\
        12. & Feber & Fever & $-0.361$ & $112586$ & $-1.94 \pm 1.76$ \\
        13. & Recept & Prescription & $-0.334$ & $5450$ & $-9.87 \pm 5.82$ \\
        14. & Centimetre & Centimetre & $-0.311$ & $12026$ & $-6.01 \pm 4.39$ \\
        15. & Knæet & The knee & $-0.300$ & $8875$ & $-6.12 \pm 5.91$ \\
        16. & Apoteket & The pharmacy & $-0.267$ & $10085$ & $-6.05 \pm 4.49$ \\
        17. & Maven & The stomach & $-0.267$ & $42105$ & $-2.36 \pm 2.82$ \\
        18. & Psykiatrisk & Psychiatric & $-0.263$ & $3688$ & $-8.99 \pm 8.49$ \\
        19. & Lungebetændelse & Pneumonia & $-0.231$ & $7597$ & $-5.79 \pm 5.62$ \\
        20. & Mavesmerter & Stomach pain & $-0.209$ & $10551$ & $-5.12 \pm 4.02$ \\
        21. & Afføring & Stool & $-0.199$ & $19155$ & $-3.40 \pm 3.27$ \\
        22. & Ribbenene & The ribs & $-0.195$ & $3928$ & $-8.26 \pm 6.18$ \\
        23. & Bløde & Bleed & $-0.194$ & $10501$ & $-4.88 \pm 3.97$ \\
        24. & Bløder & Bleeding & $-0.193$ & $24313$ & $-2.90 \pm 2.93$ \\
        25. & Ribben & Ribs & $-0.189$ & $2941$ & $-8.96 \pm 7.56$ \\
        26. & Brækket & Broken & $-0.183$ & $19415$ & $-3.49 \pm 2.83$ \\
        27. & Betændelse & Inflammation & $-0.181$ & $10050$ & $-5.27 \pm 3.30$ \\
        28. & Forkølet & Common cold & $-0.161$ & $8127$ & $-5.31 \pm 3.75$ \\
        29. & Morgen & Morning or morrow & $-0.160$ & $78558$ & $-1.23 \pm 1.70$ \\
        30. & Hævelse & Swelling & $-0.159$ & $17762$ & $-3.71 \pm 2.32$ \\

@@

% \todo[inline]{Insert table A6 here}
\begin{table}[h]
    \centering
    \caption{Overall performance of model, call takers and simulated combinations of model and call takers on MH-1813 test data.}
    \label{tab_retrospective:tableA6}
    \resizebox*{0.98\textwidth}{!}{%
    \begin{tabular}{c|c|cc|cc|cc}
        \toprule

        Predictor & Call taker & \multicolumn{2}{c|}{Model} & \multicolumn{4}{c}{Call taker supported by the model (simulated)} \\
        \midrule
        When & - & After call & During call & After call & During call & After call & During call \\
        \midrule
        Method & - & 1.C & 2.C & 1.A & 1.B & 2.A & 2.B \\
        \midrule

        F1-score [\%] $\uparrow$ & \makecell{25.8 \\ (23.7-27.9)} & \makecell{35.7 \\ (35.0-36.4)} & \makecell{33.1 \\ (32.4-33.7)} & \makecell{28.9 \\ (28.3-29.5)} & \makecell{33.3 \\ (32.5-34.1)} & \makecell{27.6 \\ (27.0-28.1)} & \makecell{32.7 \\ (31.8-33.5)} \\
        \midrule
        Sensitivity [\%] $\uparrow$ & \makecell{52.7 \\ (49.2-56.4)} & \makecell{63.0 \\ (62.0-64.1)} & \makecell{58.7 \\ (57.7-59.8)} & \makecell{72.4 \\ (71.5-73.3)} & \makecell{43.4 \\ (42.3-44.5)} & \makecell{72.3 \\ (71.4-73.3)} & \makecell{39.1 \\ (38.1-40.1)} \\
        \midrule
        PPV [\%] $\uparrow$ & \makecell{17.1 \\ (15.5-18.6)} & \makecell{24.9 \\ (24.3-25.5)} & \makecell{23.0 \\ (22.5-23.6)} & \makecell{18.0 \\ (17.6-18.4)} & \makecell{27.0 \\ (26.3-27.8)} & \makecell{17.0 \\ (16.7-17.4)} & \makecell{28.1 \\ (27.3-28.9)} \\
        \midrule
        \makecell[l]{FOR [\%] $\downarrow$ \\ (1 - specificity)} & \makecell{0.105 \\ (0.094-0.116)} & \makecell{0.082 \\ (0.079-0.085)} & \makecell{0.091 \\ (0.088-0.094)} & \makecell{0.061 \\ (0.059-0.064)} & \makecell{0.125 \\ (0.121-0.129)} & \makecell{0.061 \\ (0.059-0.064)} & \makecell{0.134 \\ (0.131-0.138)} \\
        \midrule
        \makecell[l]{FPR [\%] $\downarrow$ \\ (1 - NPV)} & \makecell{0.565 \\ (0.539-0.590)} & \makecell{0.419 \\ (0.413-0.426)} & \makecell{0.432 \\ (0.426-0.439)} & \makecell{0.726 \\ (0.717-0.735)} & \makecell{0.258 \\ (0.253-0.263)} & \makecell{0.776 \\ (0.767-0.786)} & \makecell{0.221 \\ (0.216-0.226)} \\

@@

\section{Research in context}

\subsection{Evidence before this study}

We searched the PubMed database for articles published in any language up to 9 May 2023 using the following terms: stroke AND (artificial intelligence OR machine learning OR deep learning) AND (EMS OR emergency medical services OR dispatch OR telephone). We identified 88 articles, none of which reported the results of machine learning-based stroke recognition during telephone calls.

One study assessed the potential impact of using speech classification software for stroke recognition by extrapolating results from a similar solution for recognising cardiac arrest. Several authors of this study co-authored the article; however, it did not report the results of an actual novel machine learning framework. The remaining articles primarily reported the use of machine learning in imaging diagnostics, stroke recognition using movement-tracking mobile devices, and the development of stroke recognition tools using other non-audio data.

\subsection{Added value of this study}

This study is the first to investigate the use of a machine learning framework for stroke recognition in medical helpline calls. The study's results can be replicated in other call lines and for other acute illnesses. A machine learning framework has been previously described for outof-hospital cardiac arrest; however, our results illustrate the feasibility of employing machine learning for detecting stroke - a more complex acute condition.

\subsection{Implications of all the available evidence}

Implementing the framework described in this study could lead to improved recognition of patients with stroke during initial contact with health services. Improving recognition would result in more patients being eligible for advanced stroke treatment and better overall outcomes owing to faster referral to a stroke unit.
